Automatically Splitting a Two-Stage Lambda Calculus

### 2016-01-06 paper/splitting.tex

This structure can be described with a type; for instance, the staged quickselect yields a binary search tree.
Indeed, for most of our examples in \ref{sec:examples}, inferring this type is straight-forward. 
However, we do not yet have a formal characterization of these boundary types that is defined for all \lang\ programs,
though we plan to pursue this in future work.
\footnote{Observe that in the outputs of splitting we could have omitted the {\tt roll} tag from functions or 
replaced $\inl a$ and $\inr b$ with $\tup {0,a}$ and $\tup {1,b}$, and the proof of correctness would still have gone through.
We chose the tags, however, in order to keep the typed interpretation more natural, even in absence of a formal result.
}
\end{abstrsyn}

>>>>

This structure can be described with a type; for instance, the staged quickselect yields a binary search tree.
Indeed, for most of our examples in \ref{sec:examples}, inferring this type is straight-forward. 
However, we do not yet have a formal characterization of these boundary types that is defined for all \lang\ programs,
though we plan to pursue this in future work.%
\footnote{Observe that in the outputs of splitting we could have omitted the {\tt roll} tag from functions or 
replaced $\inl a$ and $\inr b$ with $\tup {0,a}$ and $\tup {1,b}$, and the proof of correctness would still have gone through.
We chose the tags, however, in order to keep the typed interpretation more natural, even in absence of a formal result.
}
\end{abstrsyn}
